plackett_luce_monster

### 2022-07-09 inst/plackett_luce_monster.Rmd
more work

```{r}
H3 <- hyper3()
for(i in seq_len(ncol(a))){
  jj <- rep("",nrow(a))
  jj[a[,i]] <- rownames(a)
  print(jj)
}
```

>>>>

```{r,label=defineoxcam}
H3 <- function(oxcam){
  out <- hyper3()
  for(i in seq_len(ncol(a))){
    jj <- rep("",nrow(a))
    jj[a[,i]] <- rownames(a)
    out <- out + cheering3(v=jj,e=c(ox=1,cam=1,prin=2, stan=3, mass=4, harv=5, cal=6), help=c(oxcam,1,1,1,1,1))
  }
  return(out)
}
```

```{r,label=calculateoxcam,cache=TRUE}
maxp(H3(oxcam=1.8888),give=TRUE,n=6)$likes
```
